### 2022-10-01 README.Rmd
logo correct
jhs retreat

# cardioStatsUSA <img src="man/figures/logo.png" align="right" height="139" />

@@

## Why we made this

## Methods

### Weights

if counts are requested, we re-calibrate weights.

### Validation of results from the shiny application

>>>>

# cardioStatsUSA <a href="https://jhs-hwg.github.io/cardioStatsUSA/"><img src="man/figures/logo.png" align="right" height="139" /></a>

@@

## TODO list

- Write vignettes for tests of the app
- Write vignette for medication data
- Replication with AB's group
- Incorporate suppression of unreliable estimates
- Documentation/demos for R functions used in the app
- Definitions/notes for all BP variables (table S1 in manuscript)
- Tutorial videos
- Do we need to use AF weights?

## Validation of results from the shiny application
